Accelerated evolution of convective simulations

### 2018-03-15 tex/bvp_paper.tex
lots of edits

\begin{abstract}
We present a method for achieving Accelerated Evolution (AE) of convective simulations.
By probing the dynamics of convection early in simulations and adjusting the
thermal profile of the simulation appropriately, we advance simulations to
evolved states on timescales much shorter than the thermal diffusion timescale.
We study this method in the context of \RB convection. 
The solutions reached by AE similar to those reached by a slow thermal evolution, 
and AE is effective in 2D, 3D, and at low and high supercriticality.  
Extensions to more complex systems are briefly discussed.
\end{abstract}
\maketitle

@@

%%%%%%%%%%%%
%%%%%%%%%%%
% RESULTS
%%%%%%%%%%%
%%%%%%%%%%%%
\vspace{-0.5cm}
\section{Results}
\label{sec:results}
We study evolved SE solutions whose supercriticalities ($S$) are 
$S \in (1, 10^5]$ in 2D and $S \in (1, 10^4]$ in
3D. We compare their properties to
accelerated evolution (AE) runs in $S \in (1, 10^7]$ in 2D and
$S \in (1, 10^4]$ in 3D.
We refer the reader to appendix \ref{appendix:run_table} for a full list of
simulations.

\begin{figure}[t!]
\includegraphics[width=\textwidth]{./figs/oscillating_plumes.png}
\caption{. \label{fig:oscillating_plumes} }
\end{figure}

The Nusselt number (Nu) quantifies the efficiency of convective heat transport
and is defined as
\begin{equation}
\text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
 = \frac{\angles{wT - \mathcal{P}\partial_z T}}{\angles{- \mathcal{P} \partial_z T}},
\end{equation}
where the volume average of a quantity, $\eta$, is shown as $\angles{\eta}$.
When $S < 10^{3+2/3}$ in 2D and for all runs in 3D, 
the evolved system is characterized by a specific
value of Nu, as the convective heat transport reaches a temporally stationary state.
At larger values of $S$ in 2D, the value of Nu varies significantly over time,
as shown by the time traces for $S = 10^5$ (top) and $S = 10^7$ (bottom) for two
AE runs in Fig. \ref{fig:oscillating_plumes}. We find that these systems go between
states in which temperature fluctuations primarily travel in their natural buoyant
direction (as in Ia and IIa, where cold elements are falling and hot elements rise),
and states in which temperature perturbations are entrained in an upflow or downflow
with oppositely signed fluid (as in Ib and IIb, where warm fluid is pulled down by the downflow
lane, and cool fluid is pulled up by the upflow lane).  The fluid from the oppositely
signed plume pushes on the other plume such that the system goes between states in which
the fluid primarily serves to enhance convective transport (Ia and IIa), states in which
there is counterclockwise entrainment (IIa and IIb), then back to enhanced transport states
followed by clockwise entrainment.  This horizontally oscillatory motion that characterizes the
plumes provides, and the resultant time-dependent entrainment, leads to large variations in Nu over time 
As a result of our choice of no-slip
boundary conditions, the fluid never enters a full domain shearing state 
\cite{goluskin&all2014}, and the
oscillatory nature of the plumes is stable.
The 2D SE simulations exhibit the same horizontally
oscillatory behavior as the AE solutions for the same initial conditions. 
This time-dependent behavior or Nu is not seen strongly in our 3D solutions,
likely as a result of the extra degrees of freedom in which rising and falling
fluid elements can expand, reducing entrainment.

The time- and volume-averaged values of the Nusselt number (Nu), the RMS
Reynolds number (Re), and the mean temperature in AE solutions 
are shown in Fig. \ref{fig:parameter_space_comparison}a-c.
Nu, which quantifies the heat transport in evolved solutions,
is shown as a function of Ra and $S$ in Fig. \ref{fig:parameter_space_comparison}a.
The
dynamic nature of the plume structures diminishes the
scaling of the heat transport to $\text{Nu} \propto \text{Ra}^{1/5}$,
which is weaker than classic scaling laws \cite{johnston&doering2009, ahlers&all2009}.
Previous studies in 2D convection may have avoided oscillatory plumes by using
bootstrapping techniques as initial conditions for high $S$ runs.
In Fig. \ref{fig:parameter_space_comparison}b, we report 
$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  This measures the degree of
turbulence in the solution, and scales roughly as
$\text{Re} \propto \text{Ra}^{0.45}$. Each simulation shows little variance in
the value of Re over time.
Fig. \ref{fig:parameter_space_comparison}c shows the scaling of $\angles{T} - T_{\text{top}}$.
The average temperature, $\angles{T}$, is dominated by its value in the isothermal interior,
so this measurements serves as a probe of the temperature jump across the boundary
layers. As a result, we expect this measure to
scale inversely with Nu in converged solutions
where fixed-flux boundary conditions are used \cite{otero&all2002}.  We find here
that $(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$, precisely the inverse
scaling of Nu.

\begin{figure}[b]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Volume- and time-averaged measurements of the Nusselt number (Nu), the
RMS Reynolds number (Re), and the mean temperature ($\angles{T}$) for AE runs are shown in (a)-(c).
Symbols are located at the mean value of
each measurement and denote 2D (purple circles) and 3D (red stars). 
The run at $S = 10^5$ marked as a
black square is examined in more detail in Figs. \ref{fig:time_trace}, \ref{fig:oscillating_plumes},
\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
Vertical lines represent the standard deviation of the measurement,
and quantify natural variation over the averaging window. 
(a) Nu scales as Ra$^{1/5}$; above S$\geq 10^{3+2/3}$,
simulations exhibit oscillating plume structures whose heat transport fluctuates over time
as a result of temporally-varying entrainment of wrongly signed temperature perturbations
(see Fig. \ref{fig:oscillating_plumes}).  
(b) Re, which measures the level of turbulence in the evolved solution, scales as
Ra$^{0.45}$. (c) The difference between $\angles{T}$ and the value of $T$ at $z = +1/2$
is shown, and this quantity scales as Ra$^{-1/5}$, the inverse of Nu.
Relative error for measurements of (d) Nu, (e) Re, and (f) $T$ between 
AE solutions and SE solutions are shown.
The greyed area of the plots indicates the region in which only AE runs were
carried out due to computational expense. \label{fig:parameter_space_comparison} }
\end{figure}

This is a short paragraph which says 2D and 3D are the same, here.

@@

The measurements presented in Fig. \ref{fig:parameter_space_comparison} demonstrate
that AE can be powerfully employed in parameter space studies in which
large numbers of simulations are compared in a volume-averaged sense.  We now turn
our examination to a more direct comparison of AE and SE for convection at
$S = 10^5$, the time and flux evolution of which was shown in Fig. \ref{fig:time_trace}.
All comparisons that follow for these two runs occur over the times shaded in
green in Fig. \ref{fig:time_trace}a\&c. Measurements are sampled every
0.1 freefall time units for 500 total time units.

@@

\begin{figure}[b]
\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
\caption{Comparisons of the evolved thermodynamic states of an AE and SE run
at $S = 10^{5}$ are shown.  (a) Evolved horizontally- and time-averaged 
temperature profiles, as a function of height.
(b) Probability Distribution Functions (PDFs) and their integrated
Cumulative Distribution Functions (CDFs)
of point-by-point measurements of the temperature field.
(c) The percentage difference between the mean temperature profiles as a function of height.
The difference between the mean profiles is very small, O(0.5\%).
(d) The value of the Kolmogorov-Smirnov (KS) statistic, or the difference between
the AE and SE CDFs, as a function of temperature.
The small
difference in the interior temperature 
results in a large difference between the two temperature CDFs near the values
of the temperature modes.  The spread of temperature around the modes, which includes the 
fluctuations that drive convection, are nearly identical between the two runs.
\label{fig:temp_comparison} }
\end{figure}

The probability distribution functions (PDFs)
of point-by-point temperature measurements are compared for the two runs
in Fig. \ref{fig:temp_comparison}b. To construct these PDFs, 
we interpolate the temperature field
of each of these snapshots onto an evenly spaced grid, determine the
frequency distribution of all measured $T$ values, and then normalize the
distribution such that its integral is unity.  The two PDFs have noticeably
different modes, as is expected from Fig. \ref{fig:temp_comparison}a. 
Over long timescales, the 0.5\% difference between the two profiles would
disappear, as the AE solution evolves to be exactly the SE solution -- this
is evident in the asymmetry of the AE PDF near the mode
in Fig. \ref{fig:temp_comparison}b and also
the trend of the mean temperature over time in Fig. \ref{fig:time_trace}c.

One means of comparing two
PDFs to determine if they are drawn from the same underlying
sample distribution is through the use of a Kolmogorov-Smirnov (KS) test \cite{wall&jenkins2012}.
We calculate the KS statistic for a PDF of some value, $q$, as
\begin{equation}
\KS{q} = \text{CDF}_{\text{AE}}(q) - \text{CDF}_{\text{SE}}(q),
\label{eqn:ks_profile}
\end{equation}
where CDF stands for cumulative distribution function, the integral of the PDF.
A traditional Kolmogorov-Smirnov statistic is just a single value,
$\KSstat{q} = |\KS{q}|_\infty =
\text{max} |\KS{q}|$, and we use both the profile KS$(q)$ and
$\KSstat{q}$ to gain insight into the likeness of two PDFs. 
We show the KS profile in Fig. \ref{fig:temp_comparison}d, and the
CDFs used to construct it overlay the PDFs in Fig. \ref{fig:temp_comparison}b.
Near the modes of the temperature PDFs, the $\KSstat{T} = 0.495$, 
which is very large and implies that roughly half of all temperature
measurements in the SE case are greater than those in the AE case.
This difference is significant, and shows that the two PDFs are distinctly different,
but aside from this large value near the modes the KS profile has very small values,
indicating that the temperature fluctuations away from the modes in the two cases are nearly identical.

In addition to comparing the thermodynamic state achieved by the SE and AE methods,
we examine the velocities found in the evolved states.
Shown are the PDFs of 
vertical velocity (Fig. \ref{fig:pdf_comparison}a), horizontal velocity (Fig. \ref{fig:pdf_comparison}b),
and the nonlinear vertical convective flux (Fig. \ref{fig:pdf_comparison}c). 
The CDFs of each profile are overplotted, and corresponding KS profiles are
shown in Fig. \ref{fig:pdf_comparison}d-f.  We report
$\KSstat{w} = 0.00615$ (vertical velocity), $\KSstat{u} = 0.0349$ (horizontal velocity),
and $\KSstat{w(T - \angles{T}_{x,y})} = 0.0263$.
Each PDF here shows a strong peak near zero due to the no-slip, impenetrable
velocity boundary conditions (Eqn. (\ref{eqn:bcs})).
The difference in vertical velocity
and heat transport between AE and SE is negligible, which is unsurprising in light of
the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d.
The horizontal velocity shows some small deviation between the two simulations, and this
likely relates to the nature of the strength of the horizontally oscillatory motions
as we previously described in the context of suppressed Nu scaling. Thus, while
the temperature profiles are distinctly drawn from different distributions in
Fig. \ref{fig:temp_comparison}b, the profiles are similar enough that they drive
nearly identical nonlinear dynamics.

@@

\section{Extensions \& Conclusions}
\label{sec:extensions}
In this work we have studied a method of Accelerated Evolution (AE) which can
be employed to achieve rapid thermal convergence of convective simulations.  We compared
this technique to the Standard Evolution (SE) of convection through a thermal diffusion timescale and
showed that AE rapidly obtains solutions whose dynamics are similar to SE solutions.
The AE method is not only valid at low values of $S$, where SE solutions
converge quickly due to the short thermal timescale, but AE is also applicable
at high values of $S$, where SE solutions are intractable.
As discussed, 2D and 3D are identical short of the time-varying entrainment states
(Fig. \ref{fig:oscillating_plumes}), so we have restricted most of our study to 2D.
However, due to the greater computational expense of 3D runs, they stand to gain more
time savings from AE. This is a sentence about the magnitude of savings involved for
AE vs. SE (wall time + cpu hours, 2d: $10^5$, 3d: $10^4$).

@@

A further area which could benefit from AE is overshooting convection, in which
studies examine adjacent stable and convecting regions
\cite{hurlburt&all1986, brandenburg&all2005, couston&all2017}.
When the interface between the stable region
and the convecting region is stiff and motions do not cross that interface,
convective motions cannot accelerate the restratification of the stable region.
In fully-convective domains, such as those studied in this work, the thermodynamics evolve
at a more rapid rate than the thermal diffusion time across the domain due to
convective mixing.  For example, in Fig. \ref{fig:time_trace}a,
the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
despite the thermal timescale being roughly $10^4$ freefall units. However, in 
studies where there is a stable region which is not mixed by convection, the experimentalist
must either wait through a thermal diffusion time for the region to restratify
or employ other methods \cite{couston&all2017} to study evolved atmospheres.

Studies of stratified, compressible convection have much to gain through
developing and employing AE.
In many studies of stratified convection, the thermal diffusivity
is inversely proportional to the density \cite{anders&brown2017}. Thus, the
thermal timescale grows with depth in the atmosphere, and
the difficulty of achieving thermal convergence grows as simulators study more highly
stratified domains.
In order to extend AE into this regime, two additional pieces of information must be considered.
First, rather than constructing the profiles in Eqn. (\ref{eqn:bvp_ratios})
with the total flux through the domain, only the superadiabatic portion of
the flux should be considered.
Second, in addition to solving for
hydrostatic balance and thermal equilibrium, as in Eqns. (\ref{eqn:bouss_BVP_momentum})
\& (\ref{eqn:bouss_BVP_energy}), it is essential to simultaneously evolve the density
profile in a manner which conserves mass.  In a 1D boundary value problem, such as
is solved to achieve AE here, this implies the inclusion of an equation which tracks
the vertically integrated mass, and sets boundary conditions on that mass to ensure
that no mass enters or leaves the domain. [GIVE NUMBERS]

An eventual use case of AE is in robustly describing convection
in stellar evolution codes. Current state of the art stellar structure
models are the solutions of 1D simulations which parameterize convection 
using Mixing Length Theory \cite{paxton&all2011}. Recent work has taken first steps towards
understanding how to simultaneously resolve convective motions while evolving
systems through many thermal timescales, as is required when modeling the evolution of stars
over the course of stellar lifetimes.
We now know that implicit timestepping methods, while not technically bound by
CFL constraints, must resolve the convective motions for stability
\cite{viallet&all2011, viallet&all2013, viallet&all2016}, and are thus
not an ideal solution to achiving long-term system evolution.
Recently, efforts have begun to project the results of 3D simulations into 1D
models to more properly parameterize convection for stellar evolution
\cite{arnett&all2015, cristini&all2016}.
Through the
careful addition and testing of new physics, AE can be generally applied to
very large complex problems such as stellar evolution, and
shows great potential for improving our understanding of convection.

>>>>

\begin{abstract}
Modern, turbulent simulations of convection suffer from a large discrepancy between
short dynamical convective timescales and long thermal timescales of system evolution.
In this paper, we present a method of achieving Accelerated Evolution (AE) of convective simulations which
fast-forwards through the long thermal evolution of these systems, and we test the
validity of this method. The AE procedure involves measuring the dynamics of convection
early in a simulation and using its characteristics to adjust the mean thermodynamic
profile within the domain towards its evolved state. We study \RB convection as a test case for AE.  
Key evolved properties of AE solutions are measured to be within a few percent
of measurements of the same quantities in solutions which are reached through 
evolution over a full thermal timescale. We conclude with a brief discussion of useful extensions
of AE, such as to studies of stratified, compressible convection.
\end{abstract}
\maketitle

@@

%%%%%%%%%%%%
%%%%%%%%%%%
% RESULTS
%%%%%%%%%%%
%%%%%%%%%%%%
\section{Results}
\label{sec:results}
We study evolved standard evolution (SE) solutions whose supercriticalities ($S$) are 
$S \in (1, 10^5]$ in 2D and $S \in (1, 10^4]$ in
3D. We compare their properties to
accelerated evolution (AE) runs at $S \in (1, 10^7]$ in 2D and
$S \in (1, 10^4]$ in 3D.
We refer the reader to appendix \ref{appendix:run_table} for a full list of
simulations.

The Nusselt number (Nu) quantifies the efficiency of convective heat transport
and is defined as
\begin{equation}
\text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
 = \frac{\angles{wT - \mathcal{P}\partial_z T}}{\angles{- \mathcal{P} \partial_z T}},
\end{equation}
where the volume average of a quantity, $\eta$, is shown as $\angles{\eta}$.
When $S < 10^{3+2/3}$ in 2D and for all runs in 3D, 
the evolved system is characterized by a time-stationary value of Nu, and is thus
in a state of constant convective heat transport.
At larger $S$ in 2D, the value of Nu varies significantly over time,
as shown by the time traces for $S = 10^5$ (top, left) and $S = 10^7$ (bottom, left) for two
AE runs in Fig. \ref{fig:oscillating_plumes}. We find that these systems exhibit
large Nu during
states in which temperature fluctuations travel in their natural buoyant
direction (Fig. \ref{fig:oscillating_plumes}, Ia \& IIa, where cold elements fall and hot elements rise).
However, when wrongly-signed temperature perturbations are entrained in an upflow or downflow
with oppositely signed fluid, Nu is suppressed (Fig. \ref{fig:oscillating_plumes}, Ib and IIb, 
where warm fluid is pulled down by the downflow
lane, and cool fluid is drawn up by the upflow lane). The plumes in these
systems naturally oscillate over time, switching between transport being dominated
by a counterclockwise cell, as pictured in Fig. \ref{fig:oscillatin_plumes}, and
a counter-clockwise cell. Our choice of no-slip
boundary conditions prevents the fluid from entering a full domain shearing state 
\cite{goluskin&all2014}, and the
oscillatory nature of the plumes is stable.
The 2D SE simulations exhibit the same horizontally
oscillatory behavior as the AE solutions for the same initial conditions. 
This time-dependent behavior of Nu is not seen strongly in our 3D solutions,
however most 3D simulations we conducted were at low $S$ compared to the runs in
which this behavior was observed in 2D.

\begin{figure}[t!]
\includegraphics[width=\textwidth]{./figs/oscillating_plumes.png}
\caption{The time variation of the Nusselt number is shown for two AE cases at
$S = 10^5$ (top) and $S = 10^7$ (bottom). On the left, the instantaneous value of Nu
is shown as a function of time. On the right, temperature snapshots are shown for
Nu maxima (Ia \& IIa) and minima (Ib \& IIb). The suppressed value of Nu at the
minma arises from entrainment of fluid elements whose temperature perturbations
are wrongly signed (e.g., hot material going downwards and cold material going
upwards in Ib \& IIb).\vspace{-1cm} \label{fig:oscillating_plumes} }
\end{figure}

\begin{figure}[b!]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Volume- and time-averaged measurements of the Nusselt number (Nu), the
RMS Reynolds number (Re), and the mean temperature ($\angles{T}$) for AE runs are shown in (a)-(c).
Symbols are located at the mean value of
each measurement and denote 2D (purple circles) and 3D (red stars). 
The run at $S = 10^5$ marked as a
black square is examined in more detail in Figs. \ref{fig:time_trace}, \ref{fig:oscillating_plumes},
\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
Vertical lines represent the standard deviation of the measurement,
and quantify natural variation over the averaging window. 
(a) Nu scales as Ra$^{1/5}$; at high $S$ in 2D the value of Nu fluctuates over time
(see Fig. \ref{fig:oscillating_plumes}).  
(b) Re, which measures turbulence in the solution, scales as
Ra$^{0.45}$. (c) The difference between $\angles{T}$ and the value of $T$ at the fixed-temperature
top boundary is shown; this quantity scales as Ra$^{-1/5}$, the inverse of Nu.
Relative error for measurements of (d) Nu, (e) Re, and (f) $\angles{T} - T_{\text{top}}$ between 
AE solutions and SE solutions are shown.
The greyed area of the plots indicates the region in which only AE runs were
carried out due to computational expense. \label{fig:parameter_space_comparison} }
\end{figure}

The time- and volume-averaged values of Nu, the RMS
Reynolds number (Re), and the mean temperature 
are shown for AE solutions in Fig. \ref{fig:parameter_space_comparison}a-c.
Mean values are shown by the symbols (purple circles and red stars), and 
the vertical lines represent the standard deviation of the measurement over time.
Nu is shown as a function of Ra and $S$ in Fig. \ref{fig:parameter_space_comparison}a.
The dynamic nature of the plume structures (e.g., Fig. \ref{fig:oscillating_plumes})
diminishes the mean
scaling of the heat transport to $\text{Nu} \propto \text{Ra}^{1/5}$,
which is weaker than classic scaling laws \cite{johnston&doering2009, ahlers&all2009}.
Previous studies in 2D convection may have avoided these time-varying Nu states by using
bootstrapping techniques as initial conditions for high $S$ runs.
In Fig. \ref{fig:parameter_space_comparison}b, we report 
$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$ as a function of Ra and $S$.  
Re measures the degree of
turbulence in the solution, and scales roughly as
$\text{Re} \propto \text{Ra}^{0.45}$. Each simulation shows little variance in
the value of Re over time.
Fig. \ref{fig:parameter_space_comparison}c shows the scaling of $\angles{T} - T_{\text{top}}$,
the mean value of the temperature minus its value at the upper (fixed temperature) boundary.
The average temperature, $\angles{T}$, is dominated by its value in the isothermal interior,
so this measurements serves as a probe of the temperature jump across the boundary
layers. As a result, we expect this measure to
scale inversely with Nu in converged solutions
where fixed-flux boundary conditions are used \cite{otero&all2002}.  We find here
that $(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$, precisely the inverse
scaling of Nu.

@@

For the select 3D runs conducted in this study, the scaling of Nu, Re, and $\angles{T} - T_{\text{top}}$
reported in Fig. \ref{fig:parameter_space_comparison}a-c is nearly identical to the
2D simulations. Errors between AE and SE solutions in 3D fall within the same range as
errors in 2D in Fig. \ref{fig:parameter_space_comparison}d-f. AE is therefore
equally effective in both 2D and 3D, and we restrict much of our study to 2D here.

The measurements presented in Fig. \ref{fig:parameter_space_comparison} demonstrate
that AE can be powerfully employed in parameter space studies in which
large numbers of simulations are compared in a volume-averaged sense.  We now turn
our examination to a more direct comparison of AE and SE for 2D convection at
$S = 10^5$, the time and flux evolution of which was shown in Fig. \ref{fig:time_trace}.
All comparisons that follow for these two runs occur over the times shaded in
green in Fig. \ref{fig:time_trace}a\&c. Measurements are sampled every
0.1 freefall time units for 500 total time units.

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
\caption{Comparisons of the evolved thermodynamic states of an AE and SE run
at $S = 10^{5}$ are shown.  (a) Evolved horizontally- and time-averaged 
temperature profiles, as a function of height.
(b) Probability Distribution Functions (PDFs) and their integrated
Cumulative Distribution Functions (CDFs)
of point-by-point measurements of the temperature field.
(c) The percentage difference between the mean temperature profiles as a function of height.
The difference between the mean profiles is very small, O(0.5\%).
(d) The value of the Kolmogorov-Smirnov (KS) statistic, or the difference between
the AE and SE CDFs, as a function of temperature.
The small
difference in the interior temperature 
results in a large difference between the two temperature CDFs near the values
of the temperature modes.  The spread of temperature around the modes, which includes the 
fluctuations that drive convection, are nearly identical between the two runs.
\label{fig:temp_comparison} }
\end{figure}

The probability distribution functions (PDFs)
of point-by-point temperature measurements are compared for the two runs
in Fig. \ref{fig:temp_comparison}b. To construct these PDFs, 
we interpolate the full temperature field
at each measurement time onto an evenly spaced grid, determine the
frequency distribution of all $T$ values over the duration of the 500 $t_{\text{ff}}$
measurement window, and then normalize the
distribution such that its integral is unity.  The two PDFs have noticeably
different modes, as is expected from Fig. \ref{fig:temp_comparison}a. 
Over long timescales, the 0.5\% difference between the two profiles would
disappear, as the AE solution evolves to be exactly the SE solution -- this
is evident in the asymmetry of the AE PDF near the mode
in Fig. \ref{fig:temp_comparison}b and also
the trend of the mean temperature over time in Fig. \ref{fig:time_trace}c.

One means of comparing two
PDFs to determine if they are drawn from the same underlying
sample distribution is through the use of a Kolmogorov-Smirnov (KS) test \cite{wall&jenkins2012}.
We calculate the KS statistic for a PDF of some value, $q$, as
\begin{equation}
\KS{q} = \text{CDF}_{\text{AE}}(q) - \text{CDF}_{\text{SE}}(q),
\label{eqn:ks_profile}
\end{equation}
where CDF stands for cumulative distribution function, the integral of the PDF.
A traditional Kolmogorov-Smirnov statistic is just a single value,
$\KSstat{q} = |\KS{q}|_\infty =
\text{max} |\KS{q}|$, and we use both the profile KS$(q)$ and
$\KSstat{q}$ to gain insight into the likeness of two PDFs. 
We show the $\KS{T}$ in Fig. \ref{fig:temp_comparison}d, and the
CDFs used to construct it overlay the PDFs in Fig. \ref{fig:temp_comparison}b.
Near the modes of the temperature PDFs, $\KSstat{T} = 0.495$, 
which is very large and implies that roughly half of all
measurements in the AE case are at a lower $T$ than those in the SE case.
While this difference is significant, it is also expected from Fig. \ref{fig:temp_comparison}a.
Fortunately, $\KS{T}$ is very small away from the modes, 
indicating that the temperature fluctuations off of the modes, which are the primary
drivers of convective transport, are nearly identical.

In addition to comparing the thermodynamic state achieved by the SE and AE methods,
we examine the velocities and heat transport found in the evolved states.
Shown are the PDFs of 
vertical velocity ($w$, Fig. \ref{fig:pdf_comparison}a), horizontal velocity ($u$, Fig. \ref{fig:pdf_comparison}b),
and the nonlinear vertical convective flux ($w(T - \angles{T}_{x,y})$, Fig. \ref{fig:pdf_comparison}c). 
Each PDF here shows a strong peak near zero due to the no-slip, impenetrable
velocity boundary conditions (Eqn. (\ref{eqn:bcs})).
The CDFs of each profile are overplotted, and corresponding KS profiles are
shown in Fig. \ref{fig:pdf_comparison}d-f.  We report
$\KSstat{w} = 0.00615$, $\KSstat{u} = 0.0349$,
and $\KSstat{w(T - \angles{T}_{x,y})} = 0.0263$.
The difference in vertical velocity
and heat transport between AE and SE is negligible, which is unsurprising in light of
the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d.
this also confirms that the large $\KSstat{T}$ in Fig. \ref{fig:temp_comparison}d is
not of concern, and that the AE run achieves the proper convective solution.
The horizontal velocity shows some small deviation between the two simulations, and this
likely relates to the precise configuration of the convective plumes (e.g., Fig. \ref{fig:oscillating_plumes}).
We find that despite our no-slip boundary conditions, the full convective roll systems
migrate slowly to the left or the right over time, and the difference in $\KS{u}$
appears to be caused by a more prominent migration in the -x direction in the AE run
than in the SE run.

@@

\section{Extensions \& Conclusions}
\label{sec:extensions}
In this work we have studied a method of Accelerated Evolution (AE) which can
be employed to achieve rapid thermal convergence of convective simulations.  We compared
this technique to the Standard Evolution (SE) of convection through a thermal diffusion timescale and
showed that AE rapidly obtains solutions whose dynamics are similar to SE solutions.
The AE method is not only valid at low values of $S$, where SE solutions
converge quickly due to the short thermal timescale, but AE is also applicable
at high values of $S$, where SE solutions are intractable.
As discussed, AE is equally applicable in 2D and 3D, so we have restricted most of our study to 2D.
At the largest values of $S$ in which AE and SE are compared in this work, we find
time savings of nearly an order of magnitude. 
For example, in 2D and at $S = 10^5$, the
AE run took 10.78 wall hours on 256 cores ($2.8\cdot 10^3$ cpu-hours) while the 
SE run took 94 wall hours ($2.4\cdot 10^4$ cpu-hours). In 3D and at $S = 10^4$,
the AE run took 2.81 wall hours on 8192 cores ($2.3 \cdot 10^4$ cpu-hours),
while the SE run took 37.9 wall hours, or ($3.1 \cdot 10^5$ cpu-hours). As $S$ increases,
and the thermal time, $t_{\kappa}$ simultaneously increases, we anticipate the time
savings to further increase.  The increased computational expense of 3D runs compared
to 2D runs implies that 3D studies can greatly benefit from the proper implementation of AE.

@@

A further area which could benefit from AE is overshooting convection, in which
studies examine adjacent stable and convecting regions
\cite{hurlburt&all1986, brandenburg&all2005, couston&all2017}.
When the interface between the stable region
and the convecting region is stiff,
convective motions cannot accelerate the restratification of the stable region.
In fully-convective domains, such as those studied in this work, the thermodynamics evolve
at a more rapid rate than the thermal diffusion time across the domain due to
convective mixing.  For example, in Fig. \ref{fig:time_trace}a,
the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
which is roughly 40\% of a thermal timescale. However, in 
studies where there is a stable region which is not mixed by convection, the experimentalist
must either wait through a thermal diffusion time for the region to restratify
or otherwise adjust the mean profile to study evolved atmospheres \cite{couston&all2017}.

Studies of stratified, compressible convection have much to gain through
developing and employing AE.
In many studies of stratified convection, the thermal diffusivity
is inversely proportional to the density \cite{anders&brown2017}. Thus, the
thermal timescale grows with depth in the atmosphere, and
the difficulty of achieving thermal convergence grows as simulators study more highly
stratified domains. For example, in a modestly stratified atmosphere which spans three
density scale heights, the density at the bottom, and thus the thermal timescale, is a
factor of 20 greater than at the top of the domain.
In order to extend AE into this regime, two additional pieces of information must be considered.
First, rather than constructing the profiles in Eqn. (\ref{eqn:bvp_ratios})
with the total flux through the domain, only the superadiabatic portion of
the flux should be considered \cite{anders&brown2017}.
Second, in addition to solving for
hydrostatic balance and thermal equilibrium, as in Eqns. (\ref{eqn:bouss_BVP_momentum})
\& (\ref{eqn:bouss_BVP_energy}), it is essential to simultaneously evolve the density
profile in a manner which conserves mass.  In a 1D boundary value problem, such as
is solved to achieve AE here, this implies the inclusion of an equation which tracks
the vertically integrated mass, and sets boundary conditions on that mass to ensure
that no mass enters or leaves the domain.

Ideally, AE can eventually be used in robustly describing convection
in stellar evolution codes. Current state of the art stellar structure
models are the solutions of 1D simulations which parameterize convection 
using Mixing Length Theory \cite{paxton&all2011}. Recent studies have tried
to understand how to simultaneously resolve convective motions and evolve
systems through many thermal timescales, as is required when determining the
interior structure of stars over their evolving lifetimes.
We now know that implicit timestepping methods
must resolve convective motions in order to timestep with stability
\cite{viallet&all2011, viallet&all2013, viallet&all2016}, and thus
cannot achieve fast, meaningful system evolution.
Recently, efforts have begun to project the results of 3D simulations into 1D
models to more properly parameterize convection for stellar evolution
\cite{arnett&all2015, cristini&all2016}. This is precisely the technology
employed in the AE method we present here. Through the careful expansion
of AE from \RB convection to fully stratified, compressible convection with realistic
opacities, it is possible that carefully evolved stellar structure models which
use statistics from resolved convective motions, rather than parameterized 1D models,
are well within reach of modern computing tools.
